\begin{thebibliography}{99}
	
	\bibitem{GPinML}
	Rasmussen, C. E. and Williams, C. K. I. (2006). Gaussian Processes for Machine Learning. {\it MIT Press}.


	\bibitem{Titsias}
	Titsias M. K. (2009).  Variational Learning of Inducing Variables in Sparse Gaussian
	Processes.  In: {\it International Conference on Artificial Intelligence and Statistics}, pp.~567–574.

	\bibitem{BigData}
	Hensman J., Fusi N., Lawrence D. (2013).  Gaussian Processes for Big Data.  In: {\it Proceedings of the Twenty-Ninth Conference on Uncertainty in Artificial Intelligence}.

	\bibitem{SVIclassification}
	Hensman J., Matthews G., Ghahramani Z. (2015). Scalable Variational Gaussian Process Classification.  In: {\it Proceedings of the Eighteenth International Conference on Artificial Intelligence and Statistics}.

	\bibitem{ExpFamilyGeom}
	Efron B. (1978). The Geometry of Exponential Families. In: {\it The Annals of Statistics}.

	\bibitem{ProjNewton}
	Schmidt M., Kim D., Sra S. (2011). Projected Newton-Type Methods in Machine Learning. In: {\it Optimization for Machine Learning}.

	\bibitem{SAG}
	Schmidt M., Le Roux N., Bach F. (2013). Minimizing Finite Sums with the Stochastic Average Gradient. {\it Manuscript}.

	\bibitem{JaakkolaJordan}
	Jaakkola T., Jordan M. (1996). A Variational Approach to Bayesian Logistic Regression Models and Their Extensions. In: {\it Artificial Intelligence and Statistics}.

	\bibitem{OldSparseMethods}
	Quinonero-Candela, J. and Rasmussen, C. (2005). A Unifying View of Sparse Approximate Gaussian Process Regression. In: {\it Journal of Machine Learning Research}

	\bibitem{SparseExperiments}
	Chalupka K., Williams C., Murray I. (2013). A Framework for Evaluating Approximation Methods for Gaussian Process Regression. In: {\it Journal of Machine Learning Research}

	\bibitem{VarBayes}
	Jaakkola, T. (2001). Tutorial on Variational Approximation Methods. In: {\it M. Opper and D. Saad (Eds.), Advances in Mean Field Methods}


\end{thebibliography}	